Using Monte Carlo to estimate the effects of NHL rule changes

### 2020-12-10 slides.Rmd
added more slides

---
title: "insert title here"
author:
output: slidy_presentation 
---

@@

- Each team plays 82 games per season
- This allows for every team to play each team at least twice
- The league is split up into two conferences, the East and the West, each with two divisions
-The East has the Metropolitan and the Atlantic divisions while the West has the Central and Pacific divisions.

@@

![Quality Metric](Images/teamQuality.png)
![Game Performance](Images/teamPerformance.png)

@@

- We have found

>>>>

---
title: "Using Monte Carlo to estimate the effects of NHL rule changes"
author: "Kilbourne Charrier, Michael Bowers, Clinton, Sam"
output: slidy_presentation 
---

@@

- Each team plays 82 games per season
- This allows for every team to play each team at least twice
- The league is split up into two conferences, the East and the West, each with two divisions
- The East has the Metropolitan and the Atlantic divisions while the West has the Central and Pacific divisions.

@@

![](Images/teamQuality.png)
![](Images/teamPerformance.png)

@@

- We have found a noticably large conference gap, with the mean of the old alignment being about -0.32 and the mean of the new alignment being about 2.18.

![](Images/GapVis.png)

- Another interesting graph!

![](Images/SeedPlace.png)
